---
output: github_document
# rmarkdown::render("README.Rmd")
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Blog-en

<!-- badges: start -->

<!-- badges: end -->

In this repository you can find the code used to generate my blog (in English): https://beamilz.com/


The blog was created using [Quarto](https://quarto.org/). You can find more info on how to create a blog with Quarto in the [documentation](https://quarto.org/docs/websites/website-blog.html).

The deploy is made with [Netlify](https://www.netlify.com/), and the comments use [giscus](https://giscus.app/).


```{r echo=FALSE}
number_of_posts <- fs::dir_ls("posts/", type = "directory") |> length()

number_of_talks <- fs::dir_ls("talks/", type = "directory") |> length()
```


As by `r format(Sys.Date(), "%B %d,  %Y")`, this blog has **`r number_of_posts` blog posts** and content from **`r number_of_talks` talks/presentations**.


